Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
use emph
Misc fixes on references
update api

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handle request asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.
As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not.

@@

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \emph{/parameter}
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \emph{/timestep}
    \end{itemize}
    \item location
    \begin{itemize}
        \item \emph{/location/point}
        \item \emph{/location/regularGrid}
    \end{itemize}
    \item timeseries
\end{itemize}

@@

\emph{Extensions} endpoints for configure extensions.

These details describes in the section \ref{se:data_preprocess}.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handle request asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in the figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. But as shown in figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

@@

\emph{Timeseries} endpoints allow to interact with Metadata Adapter, and those are cache on the Query Handler in order to perform search queries.
\begin{itemize}
    \item parameter
    \begin{itemize}
        \item \emph{GET /parameter} - Get parameters
        \item \emph{POST /parameter} - Create parameter
        \item \emph{PUT /parameter/id} - Update parameter
        \item \emph{DELETE /parameter/id} - Delete parameter
    \end{itemize}
    \item timeStep
    \begin{itemize}
        \item \emph{GET timestep} - Get TimeSteps
        \item \emph{POST timestep} - Create TimeStep
        \item \emph{PUT timestep/id} - Update TimeStep
        \item \emph{DELETE timestep/id} - Delete TimeStep
    \end{itemize}
    \item location
    \begin{itemize}
        \item \emph{GET /location} - Get location points
        \item \emph{POST /location} - Create location point
        \item \emph{PUT /location/id} - Update location point
        \item \emph{DELETE /location/id} - Delete location point
        \item \emph{GET /location/regular-grid} - Get regular grids
        \item \emph{POST /location/regular-grid} - Create regular grid
        \item \emph{PUT /location/regular-grid/id} - Update regular grid
        \item \emph{DELETE /location/regular-grid/id} - Delete regular grid
    \end{itemize}
    \item timeseries
    \begin{itemize}
        \item \emph{GET /timeseries} - Get timeseries
        \item \emph{POST /timeseries} - Create timeseries
        \item \emph{PUT /timeseries/id} - Update timeseries
        \item \emph{DELETE /timeseries/id} - Delete timeseries
    \end{itemize}
\end{itemize}

@@

\emph{Extensions} endpoints for configure extensions. These details describes in the section \ref{se:data_preprocess}.
